---
title: "Data621 Assignment 5"
author: "Ritesh Lohiya"
date: "July 12, 2018"
output: html_document
---

#Overview

In this homework assignment, you will explore, analyze and model a data set containing information on approximately 12,000 commercially available wines. The variables are mostly related to the chemical properties of the wine being sold. The response variable is the number of sample cases of wine that were purchased by wine distribution companies after sampling a wine. These cases would be used to provide tasting samples to restaurants and wine stores around the United States. The more sample cases purchased, the more likely is a wine to be sold at a high end restaurant. A large wine manufacturer is studying the data in order to predict the number of wine cases ordered based upon the wine characteristics. If the wine manufacturer can predict the number of cases, then that manufacturer will be able to adjust their wine offering to maximize sales. Your objective is to build a count regression model to predict the number of cases of wine that will be sold given certain properties of the wine. HINT: Sometimes, the fact that a variable is missing is actually predictive of the target. You can only use the variables given to you (or variables that you derive from the variables provided). Below is a short description of the variables of interest in the data set:

#install.packages('corrplot')

```{r}
library(readr)
library(kableExtra)
library(tidyverse)
library(knitr)
library(psych)
library(gridExtra)
library(usdm)
library(mice)
library(ggiraph)
library(cowplot)
library(reshape2)
library(corrgram)
library(caTools)
library(caret)
library(ROCR)
library(pROC)
library(reshape2)
library(Amelia)
library(qqplotr)
library(moments)
library(car)
library(MASS)
library(geoR)
library(pander)
```

#DATA EXPLORATION:

```{r}
wine_train <- read.csv("https://raw.githubusercontent.com/Riteshlohiya/Data621-Assignment-5/master/wine_training_data.csv", stringsAsFactors = FALSE) 

do_factors <- function(wine_instance){
  wine_instance <- within(wine_instance, {
      LabelAppeal <- factor(LabelAppeal)
      AcidIndex <- factor(AcidIndex)
      STARS <- factor(STARS)
  })
  return (wine_instance)
}
summary(wine_train)
```

Removing the Index column:

```{r}
wine_train <- wine_train[,-c(1)]
```


There are 12795 observations and 16 variables. Each wine has 14 potential predictor variables, and 1 response variable. The response variable is "TARGET", which is the number of cases purchased.

Visual Exploration:

Let's dig into our response variables.

Response Variable AcidIndex - Proprietary method of testing total acidity of wine by using a weighted average.

```{r}
with(wine_train, c(summary(AcidIndex), SD=sd(AcidIndex), Skew=skewness(AcidIndex), Kurt=kurtosis(AcidIndex)))

hist <- ggplot(wine_train, aes(AcidIndex)) + geom_histogram(fill = 'dodgerblue', binwidth = 2, color = 'darkgray' ) + 
 theme_classic() + labs(title = 'Histogram of AcidIndex') + theme(plot.title = element_text(hjust = 0.5)) 

qq_plot <- ggplot(wine_train, aes(sample=AcidIndex)) + stat_qq_point(color='dodgerblue') + stat_qq_line(color='darkgray') +
  labs(x="Thoretical Quantiles", y="Sample Quantiles", title = "QQ Plot of AcidIndex") + theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5)) 

box_plot <- ggplot(wine_train, aes(x="", AcidIndex)) + geom_boxplot(fill='dodgerblue', color='darkgray')+ theme_classic() +
  labs(title = 'Boxplot of AcidIndex', x="") + theme(plot.title = element_text(hjust = 0.5)) + coord_flip()

box_TARGET <- ggplot(wine_train, aes(x=factor(TARGET), AcidIndex)) + geom_boxplot(fill='dodgerblue', color='darkgrey') +
  labs(x='TARGET', title = 'Boxplot of AcidIndex by TARGET') + theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) 

grid.arrange(hist, qq_plot, box_plot, box_TARGET, ncol=2)
```

Response Variable Alcohol - This variable tells us about the Alcohol content.

```{r}
with(wine_train, c(summary(Alcohol), SD=sd(Alcohol), Skew=skewness(Alcohol), Kurt=kurtosis(Alcohol)))

hist <- ggplot(wine_train, aes(Alcohol)) + geom_histogram(fill = 'dodgerblue', binwidth = 2, color = 'darkgray' ) + 
 theme_classic() + labs(title = 'Histogram of Alcohol') + theme(plot.title = element_text(hjust = 0.5)) 

qq_plot <- ggplot(wine_train, aes(sample=Alcohol)) + stat_qq_point(color='dodgerblue') + stat_qq_line(color='darkgray') +
  labs(x="Thoretical Quantiles", y="Sample Quantiles", title = "QQ Plot of Alcohol") + theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5)) 

box_plot <- ggplot(wine_train, aes(x="", Alcohol)) + geom_boxplot(fill='dodgerblue', color='darkgray')+ theme_classic() +
  labs(title = 'Boxplot of Alcohol', x="") + theme(plot.title = element_text(hjust = 0.5)) + coord_flip()

box_TARGET <- ggplot(wine_train, aes(x=factor(TARGET), Alcohol)) + geom_boxplot(fill='dodgerblue', color='darkgrey') +
  labs(x='TARGET', title = 'Boxplot of Alcohol by TARGET') + theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) 

grid.arrange(hist, qq_plot, box_plot, box_TARGET, ncol=2)
```

Response Variable Chlorides - This variable tells us about the Chloride content of wine.

```{r}
with(wine_train, c(summary(Chlorides), SD=sd(Chlorides), Skew=skewness(Chlorides), Kurt=kurtosis(Chlorides)))

hist <- ggplot(wine_train, aes(Chlorides)) + geom_histogram(fill = 'dodgerblue', binwidth = .2, color = 'darkgray' ) + 
 theme_classic() + labs(title = 'Histogram of Chlorides') + theme(plot.title = element_text(hjust = 0.5)) 

qq_plot <- ggplot(wine_train, aes(sample=Chlorides)) + stat_qq_point(color='dodgerblue') + stat_qq_line(color='darkgray') +
  labs(x="Thoretical Quantiles", y="Sample Quantiles", title = "QQ Plot of Chlorides") + theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5)) 

box_plot <- ggplot(wine_train, aes(x="", Chlorides)) + geom_boxplot(fill='dodgerblue', color='darkgray')+ theme_classic() +
  labs(title = 'Boxplot of Chlorides', x="") + theme(plot.title = element_text(hjust = 0.5)) + coord_flip()

box_TARGET <- ggplot(wine_train, aes(x=factor(TARGET), Chlorides)) + geom_boxplot(fill='dodgerblue', color='darkgrey') +
  labs(x='TARGET', title = 'Boxplot of Chlorides by TARGET') + theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) 

grid.arrange(hist, qq_plot, box_plot, box_TARGET, ncol=2)
```

Response Variable CitricAcid - This variable tells us about the Citric Acid Content of wine.

```{r}
with(wine_train, c(summary(CitricAcid), SD=sd(CitricAcid), Skew=skewness(CitricAcid), Kurt=kurtosis(CitricAcid)))

hist <- ggplot(wine_train, aes(CitricAcid)) + geom_histogram(fill = 'dodgerblue', binwidth = 1, color = 'darkgray' ) + 
 theme_classic() + labs(title = 'Histogram of CitricAcid') + theme(plot.title = element_text(hjust = 0.5)) 

qq_plot <- ggplot(wine_train, aes(sample=CitricAcid)) + stat_qq_point(color='dodgerblue') + stat_qq_line(color='darkgray') +
  labs(x="Thoretical Quantiles", y="Sample Quantiles", title = "QQ Plot of CitricAcid") + theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5)) 

box_plot <- ggplot(wine_train, aes(x="", CitricAcid)) + geom_boxplot(fill='dodgerblue', color='darkgray')+ theme_classic() +
  labs(title = 'Boxplot of CitricAcid', x="") + theme(plot.title = element_text(hjust = 0.5)) + coord_flip()

box_TARGET <- ggplot(wine_train, aes(x=factor(TARGET), CitricAcid)) + geom_boxplot(fill='dodgerblue', color='darkgrey') +
  labs(x='TARGET', title = 'Boxplot of CitricAcid by TARGET') + theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) 

grid.arrange(hist, qq_plot, box_plot, box_TARGET, ncol=2)
```

Response Variable Density - This variable tells us about the Density of wine.

```{r}
with(wine_train, c(summary(Density), SD=sd(Density), Skew=skewness(Density), Kurt=kurtosis(Density)))

hist <- ggplot(wine_train, aes(Density)) + geom_histogram(fill = 'dodgerblue', binwidth = .05, color = 'darkgray' ) + 
 theme_classic() + labs(title = 'Histogram of Density') + theme(plot.title = element_text(hjust = 0.5)) 
qq_plot <- ggplot(wine_train, aes(sample=Density)) + stat_qq_point(color='dodgerblue') + stat_qq_line(color='darkgray') +
  labs(x="Thoretical Quantiles", y="Sample Quantiles", title = "QQ Plot of Density") + theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5)) 

box_plot <- ggplot(wine_train, aes(x="", Density)) + geom_boxplot(fill='dodgerblue', color='darkgray')+ theme_classic() +
  labs(title = 'Boxplot of Density', x="") + theme(plot.title = element_text(hjust = 0.5)) + coord_flip()

box_TARGET <- ggplot(wine_train, aes(x=factor(TARGET), Density)) + geom_boxplot(fill='dodgerblue', color='darkgrey') +
  labs(x='TARGET', title = 'Boxplot of Density by TARGET') + theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) 

grid.arrange(hist, qq_plot, box_plot, box_TARGET, ncol=2)
```

Response Variable FixedAcidity - This variable tells us about the FixedAcidity of wine.

```{r}
with(wine_train, c(summary(FixedAcidity), SD=sd(FixedAcidity), Skew=skewness(FixedAcidity), Kurt=kurtosis(FixedAcidity)))

hist <- ggplot(wine_train, aes(FixedAcidity)) + geom_histogram(fill = 'dodgerblue', binwidth = 4, color = 'darkgray' ) + 
 theme_classic() + labs(title = 'Histogram of FixedAcidity') + theme(plot.title = element_text(hjust = 0.5)) 

qq_plot <- ggplot(wine_train, aes(sample=FixedAcidity)) + stat_qq_point(color='dodgerblue') + stat_qq_line(color='darkgray') +
  labs(x="Thoretical Quantiles", y="Sample Quantiles", title = "QQ Plot of FixedAcidity") + theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5)) 

box_plot <- ggplot(wine_train, aes(x="", FixedAcidity)) + geom_boxplot(fill='dodgerblue', color='darkgray')+ theme_classic() +
  labs(title = 'Boxplot of FixedAcidity', x="") + theme(plot.title = element_text(hjust = 0.5)) + coord_flip()

box_TARGET <- ggplot(wine_train, aes(x=factor(TARGET), FixedAcidity)) + geom_boxplot(fill='dodgerblue', color='darkgrey') +
  labs(x='TARGET', title = 'Boxplot of FixedAcidity by TARGET') + theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) 

grid.arrange(hist, qq_plot, box_plot, box_TARGET, ncol=2)
```

Response Variable FreeSulfurDioxide - This variable tells us about the Sulfur Dioxide content of wine.

```{r}
with(wine_train, c(summary(FreeSulfurDioxide), SD=sd(FreeSulfurDioxide), Skew=skewness(FreeSulfurDioxide), Kurt=kurtosis(FreeSulfurDioxide)))

hist <- ggplot(wine_train, aes(FreeSulfurDioxide)) + geom_histogram(fill = 'dodgerblue', binwidth = 50, color = 'darkgray' ) + 
 theme_classic() + labs(title = 'Histogram of FreeSulfurDioxide') + theme(plot.title = element_text(hjust = 0.5)) 

qq_plot <- ggplot(wine_train, aes(sample=FreeSulfurDioxide)) + stat_qq_point(color='dodgerblue') + stat_qq_line(color='darkgray') +
  labs(x="Thoretical Quantiles", y="Sample Quantiles", title = "QQ Plot of FreeSulfurDioxide") + theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5)) 

box_plot <- ggplot(wine_train, aes(x="", FreeSulfurDioxide)) + geom_boxplot(fill='dodgerblue', color='darkgray')+ theme_classic() +
  labs(title = 'Boxplot of FreeSulfurDioxide', x="") + theme(plot.title = element_text(hjust = 0.5)) + coord_flip()

box_TARGET <- ggplot(wine_train, aes(x=factor(TARGET), FreeSulfurDioxide)) + geom_boxplot(fill='dodgerblue', color='darkgrey') +
  labs(x='TARGET', title = 'Boxplot of FreeSulfurDioxide by TARGET') + theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) 

grid.arrange(hist, qq_plot, box_plot, box_TARGET, ncol=2)
```

Response Variable LabelAppeal - Marketing Score indicating the appeal of label design for consumers. High numbers suggest customers like the label design. Negative numbers suggest customes don't like the design. Many consumers purchase based on the visual appeal of the wine label design. Higher numbers suggest better sales.

```{r}
with(wine_train, c(summary(LabelAppeal), SD=sd(LabelAppeal), Skew=skewness(LabelAppeal), Kurt=kurtosis(LabelAppeal)))

hist <- ggplot(wine_train, aes(LabelAppeal)) + geom_histogram(fill = 'dodgerblue', binwidth = 1, color = 'darkgray' ) + 
 theme_classic() + labs(title = 'Histogram of LabelAppeal') + theme(plot.title = element_text(hjust = 0.5)) 

qq_plot <- ggplot(wine_train, aes(sample=LabelAppeal)) + stat_qq_point(color='dodgerblue') + stat_qq_line(color='darkgray') +
  labs(x="Thoretical Quantiles", y="Sample Quantiles", title = "QQ Plot of LabelAppeal") + theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5)) 

box_plot <- ggplot(wine_train, aes(x="", LabelAppeal)) + geom_boxplot(fill='dodgerblue', color='darkgray')+ theme_classic() +
  labs(title = 'Boxplot of LabelAppeal', x="") + theme(plot.title = element_text(hjust = 0.5)) + coord_flip()

box_TARGET <- ggplot(wine_train, aes(x=factor(TARGET), LabelAppeal)) + geom_boxplot(fill='dodgerblue', color='darkgrey') +
  labs(x='TARGET', title = 'Boxplot of LabelAppeal by TARGET') + theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) 

grid.arrange(hist, qq_plot, box_plot, box_TARGET, ncol=2)
```

Response Variable ResidualSugar - This variable tells us about the ResidualSugar of wine.

```{r}
with(wine_train, c(summary(ResidualSugar), SD=sd(ResidualSugar), Skew=skewness(ResidualSugar), Kurt=kurtosis(ResidualSugar)))

hist <- ggplot(wine_train, aes(ResidualSugar)) + geom_histogram(fill = 'dodgerblue', binwidth = 20, color = 'darkgray' ) + 
 theme_classic() + labs(title = 'Histogram of ResidualSugar') + theme(plot.title = element_text(hjust = 0.5)) 

qq_plot <- ggplot(wine_train, aes(sample=ResidualSugar)) + stat_qq_point(color='dodgerblue') + stat_qq_line(color='darkgray') +
  labs(x="Thoretical Quantiles", y="Sample Quantiles", title = "QQ Plot of ResidualSugar") + theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5)) 

box_plot <- ggplot(wine_train, aes(x="", ResidualSugar)) + geom_boxplot(fill='dodgerblue', color='darkgray')+ theme_classic() +
  labs(title = 'Boxplot of ResidualSugar', x="") + theme(plot.title = element_text(hjust = 0.5)) + coord_flip()

box_TARGET <- ggplot(wine_train, aes(x=factor(TARGET), ResidualSugar)) + geom_boxplot(fill='dodgerblue', color='darkgrey') +
  labs(x='TARGET', title = 'Boxplot of ResidualSugar by TARGET') + theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) 

grid.arrange(hist, qq_plot, box_plot, box_TARGET, ncol=2)
```

Response Variable STARS - Wine rating by a team of experts. 4 Stars = Excellent, 1 Star = Poor. A high number of stars suggests high sales.

```{r}
with(wine_train, c(summary(STARS), SD=sd(STARS), Skew=skewness(STARS), Kurt=kurtosis(STARS)))

hist <- ggplot(wine_train, aes(STARS)) + geom_histogram(fill = 'dodgerblue', binwidth = 1, color = 'darkgray' ) + 
 theme_classic() + labs(title = 'Histogram of STARS') + theme(plot.title = element_text(hjust = 0.5)) 

qq_plot <- ggplot(wine_train, aes(sample=STARS)) + stat_qq_point(color='dodgerblue') + stat_qq_line(color='darkgray') +
  labs(x="Thoretical Quantiles", y="Sample Quantiles", title = "QQ Plot of STARS") + theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5)) 

box_plot <- ggplot(wine_train, aes(x="", STARS)) + geom_boxplot(fill='dodgerblue', color='darkgray')+ theme_classic() +
  labs(title = 'Boxplot of STARS', x="") + theme(plot.title = element_text(hjust = 0.5)) + coord_flip()

box_TARGET <- ggplot(wine_train, aes(x=factor(TARGET), STARS)) + geom_boxplot(fill='dodgerblue', color='darkgrey') +
  labs(x='TARGET', title = 'Boxplot of STARS by TARGET') + theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) 

grid.arrange(hist, qq_plot, box_plot, box_TARGET, ncol=2)
```

Response Variable Sulphates - This variable tells us about the Sulphates content of wine.

```{r}
with(wine_train, c(summary(Sulphates), SD=sd(Sulphates), Skew=skewness(Sulphates), Kurt=kurtosis(Sulphates)))

hist <- ggplot(wine_train, aes(Sulphates)) + geom_histogram(fill = 'dodgerblue', binwidth = .5, color = 'darkgray' ) + 
 theme_classic() + labs(title = 'Histogram of Sulphates') + theme(plot.title = element_text(hjust = 0.5)) 

qq_plot <- ggplot(wine_train, aes(sample=Sulphates)) + stat_qq_point(color='dodgerblue') + stat_qq_line(color='darkgray') +
  labs(x="Thoretical Quantiles", y="Sample Quantiles", title = "QQ Plot of Sulphates") + theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5)) 

box_plot <- ggplot(wine_train, aes(x="", Sulphates)) + geom_boxplot(fill='dodgerblue', color='darkgray')+ theme_classic() +
  labs(title = 'Boxplot of Sulphates', x="") + theme(plot.title = element_text(hjust = 0.5)) + coord_flip()

box_TARGET <- ggplot(wine_train, aes(x=factor(TARGET), Sulphates)) + geom_boxplot(fill='dodgerblue', color='darkgrey') +
  labs(x='TARGET', title = 'Boxplot of Sulphates by TARGET') + theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) 

grid.arrange(hist, qq_plot, box_plot, box_TARGET, ncol=2)
```


Response Variable TotalSulfurDioxide - This variable tells us about the Total Sulfur Dioxide of Wine.

```{r}
with(wine_train, c(summary(TotalSulfurDioxide), SD=sd(TotalSulfurDioxide), Skew=skewness(TotalSulfurDioxide), Kurt=kurtosis(TotalSulfurDioxide)))

hist <- ggplot(wine_train, aes(TotalSulfurDioxide)) + geom_histogram(fill = 'dodgerblue', binwidth = 200, color = 'darkgray' ) + 
 theme_classic() + labs(title = 'Histogram of TotalSulfurDioxide') + theme(plot.title = element_text(hjust = 0.5)) 

qq_plot <- ggplot(wine_train, aes(sample=TotalSulfurDioxide)) + stat_qq_point(color='dodgerblue') + stat_qq_line(color='darkgray') +
  labs(x="Thoretical Quantiles", y="Sample Quantiles", title = "QQ Plot of TotalSulfurDioxide") + theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5)) 

box_plot <- ggplot(wine_train, aes(x="", TotalSulfurDioxide)) + geom_boxplot(fill='dodgerblue', color='darkgray')+ theme_classic() +
  labs(title = 'Boxplot of TotalSulfurDioxide', x="") + theme(plot.title = element_text(hjust = 0.5)) + coord_flip()

box_TARGET <- ggplot(wine_train, aes(x=factor(TARGET), TotalSulfurDioxide)) + geom_boxplot(fill='dodgerblue', color='darkgrey') +
  labs(x='TARGET', title = 'Boxplot of TotalSulfurDioxide by TARGET') + theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) 

grid.arrange(hist, qq_plot, box_plot, box_TARGET, ncol=2)
```

Response Variable VolatileAcidity - This variable tells us about the VolatileAcidity content of Wine.

```{r}
with(wine_train, c(summary(VolatileAcidity), SD=sd(VolatileAcidity), Skew=skewness(VolatileAcidity), Kurt=kurtosis(VolatileAcidity)))

hist <- ggplot(wine_train, aes(VolatileAcidity)) + geom_histogram(fill = 'dodgerblue', binwidth = .5, color = 'darkgray' ) + 
 theme_classic() + labs(title = 'Histogram of VolatileAcidity') + theme(plot.title = element_text(hjust = 0.5)) 

qq_plot <- ggplot(wine_train, aes(sample=VolatileAcidity)) + stat_qq_point(color='dodgerblue') + stat_qq_line(color='darkgray') +
  labs(x="Thoretical Quantiles", y="Sample Quantiles", title = "QQ Plot of VolatileAcidity") + theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5)) 

box_plot <- ggplot(wine_train, aes(x="", VolatileAcidity)) + geom_boxplot(fill='dodgerblue', color='darkgray')+ theme_classic() +
  labs(title = 'Boxplot of VolatileAcidity', x="") + theme(plot.title = element_text(hjust = 0.5)) + coord_flip()

box_TARGET <- ggplot(wine_train, aes(x=factor(TARGET), VolatileAcidity)) + geom_boxplot(fill='dodgerblue', color='darkgrey') +
  labs(x='TARGET', title = 'Boxplot of VolatileAcidity by TARGET') + theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) 

grid.arrange(hist, qq_plot, box_plot, box_TARGET, ncol=2)
```

Response Variable pH - This variable tells us about the pH of Wine.

```{r}
with(wine_train, c(summary(pH), SD=sd(pH), Skew=skewness(pH), Kurt=kurtosis(pH)))

hist <- ggplot(wine_train, aes(pH)) + geom_histogram(fill = 'dodgerblue', binwidth = .5, color = 'darkgray' ) + 
 theme_classic() + labs(title = 'Histogram of pH') + theme(plot.title = element_text(hjust = 0.5)) 

qq_plot <- ggplot(wine_train, aes(sample=pH)) + stat_qq_point(color='dodgerblue') + stat_qq_line(color='darkgray') +
  labs(x="Thoretical Quantiles", y="Sample Quantiles", title = "QQ Plot of pH") + theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5)) 

box_plot <- ggplot(wine_train, aes(x="", pH)) + geom_boxplot(fill='dodgerblue', color='darkgray')+ theme_classic() +
  labs(title = 'Boxplot of pH', x="") + theme(plot.title = element_text(hjust = 0.5)) + coord_flip()

box_TARGET <- ggplot(wine_train, aes(x=factor(TARGET), pH)) + geom_boxplot(fill='dodgerblue', color='darkgrey') +
  labs(x='TARGET', title = 'Boxplot of pH by TARGET') + theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) 

grid.arrange(hist, qq_plot, box_plot, box_TARGET, ncol=2)
```

Now lets see NA's for all the variables other than STARS.STARS has NAs that is more than 10%.


```{r}
Non_NAs <- sapply(wine_train, function(y) sum(length(which(!is.na(y)))))
NAs <- sapply(wine_train, function(y) sum(length(which(is.na(y)))))
NA_Percent <- NAs / (NAs + Non_NAs)

NA_SUMMARY <- data.frame(Non_NAs,NAs,NA_Percent)

missmap(wine_train, main = "Missing Values")

kable(NA_SUMMARY)
```

Finding correlations: The correlation plot below shows how variables in the dataset are related to each other. Looking at the plot, we dont see much correlations.

```{r}
names(wine_train)
cor(drop_na(wine_train))
```

```{r}
pairs.panels(wine_train[1:15]) 
``` 


 



















